### 2019-08-09 thesis.tex
*** empty log message ***

As soon as the pervasiveness of the plasma state in space came as a fact,
plasma physics began to be recognized as an essential component in the
multidisciplinary framework of astrophysics \cite{Alfven1950,Parker1956,
  Alfven1961,Gailitis1964,Alfven1971}. At the same time, the analysis and
interpretation of observational data started to have increasing relevance
in the progress of theoretical, computational, and experimental plasma
physics research \cite{YZKS16,Donnert2014,Pezzi2018,Howes2018,Peterson2019}.
In this context of mutual collaboration, the solar and interplanetary
plasma research has a pivotal contribution. The accessibility to direct,
in situ measurements, highly resolved remote sensing and high-resolution
spectroscopy, turned the solar system into a space plasma laboratory.
Processes like magnetic reconnection, particle acceleration, shocks, and
turbulence can be "closely" observed by space probes, and the understanding
acquired may be extended or adapted to address similar phenomena observed
in remote astrophysical environments \cite{NAP10477}.

@@

\section{Solar and space physics}
\label{sec:solar-physics}
The domain of solar and space physics is the \emph{heliosphere}, a cavity in
the interstellar medium, created by the constant supersonic flow of solar
plasma that permeates the interplanetary space. This region encloses the solar
system and extends for approximately $140\unit{AU}$ in the surrounding galactic
space. Its outer limit is the \emph{heliopause}, an interface zone where the
outgoing pressure of the solar plasma balances the incoming pressure from the
interstellar medium. This comet-shaped plasma bubble, has an inner boundary, the
\emph{termination shock}, which delimits the sphere of absolute influence of the
solar plasma. Outside the termination shock, the solar wind particles start to
be subjected to increasing external pressure, transitioning to a subsonic flow
that blends with the interstellar medium at roughly $100\unit{AU}$ from the Sun.
Beyond the termination shock, lies the heliosheath, a so-far-unexplored zone
that extends out to the heliopause, separating the solar domain from the nearby
galactic region \cite{NAP13060}. In \autoref{figD1}, we have a depiction of the
regions and boundaries described above, and the current location of both Voyager
missions, that are already outside the heliosphere, in the interstellar space.
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{solar_system_env.png}
    \caption{Main boundaries of the heliosphere and the location of both
      Voyager missions.}
      {\footnotesize Credit:}
      \href{https://voyager.jpl.nasa.gov/news/details.php?article_id=112}
      {\footnotesize NASA/JPL-Caltech}{\footnotesize , accessed at 08/08/2019.}
    \label{figD1}
  \end{center}
\end{figure}

Solar physics can be thought of as a combination of plasma and space physics.

>>>>

As soon as the pervasiveness of the plasma state in space came as a fact,
plasma physics began to be recognized as an essential component in the
multidisciplinary framework of astrophysics \cite{Alfven1950,Parker1956,
  Alfven1961,Gailitis1964,Alfven1971}. At the same time, the analysis and
interpretation of observational data started to have increasing relevance
in the progress of theoretical, computational, and experimental plasma
physics research \cite{YZKS16,Donnert2014,Pezzi2018,Howes2018,Peterson2019}.
In this context of mutual collaboration, the solar and interplanetary
plasma research has a pivotal contribution. The accessibility to direct,
in situ measurements, highly resolved remote sensing and high-resolution
spectroscopy, turned the solar system into a space plasma laboratory.
Processes like magnetic reconnection, particle acceleration, shocks, and
turbulence can be closely observed by space probes, and the understanding
acquired may be extended or adapted to address similar phenomena observed
in remote astrophysical environments \cite{NAP10477}.

@@

\section{Solar and space physics}
\label{sec:solar-physics}
The domain of solar and space physics is the \emph{heliosphere}, a cavity in
the interstellar medium, created by the constant supersonic flow of solar
plasma that permeates the interplanetary space. This region encloses the solar
system and extends for approximately $140\unit{AU}$\footnote{$1\unit{AU}=150
  \times 10^6\unit{km}$, where AU means \emph{astronomical unit}, which is
  defined as the mean distance between the Sun and the Earth.} in the
surrounding galactic space. Its outer limit is the \emph{heliopause}, an
interface zone where the outgoing pressure of the solar plasma balances the
incoming pressure from the interstellar medium. This comet-shaped plasma bubble
\cite{Dialynas2017}, has an inner boundary, the \emph{termination shock}, which
delimits the sphere of absolute influence of the solar plasma. Beyond the
termination shock, at roughly $100\unit{AU}$ from the Sun, extending out to the
heliopause, is the heliosheath. In this region, the solar wind particles start
being subjected to increasing external pressure, transitioning to a subsonic,
turbulent flow that blends and interacts directly with the matter in the local
interstellar medium \cite{NAP13060}. In \autoref{figD1}, we have a depiction of
the regions and boundaries described above, and the current location of both
Voyager missions, that are already outside the heliosphere, in the interstellar
space.
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{solar_system_env.png}
    \caption{Main boundaries of the heliosphere and the location of both
      Voyager missions.}
      {\footnotesize Credit:}
      \href{https://voyager.jpl.nasa.gov/news/details.php?article_id=112}
      {\footnotesize NASA/JPL-Caltech}{\footnotesize , accessed at 08/08/2019.}
    \label{figD1}
  \end{center}
\end{figure}

As described above, particles ejected by the Sun determine the overall
dynamics of the interplanetary space until the termination shock boundary.
Beyond this boundary, the solar wind still has a significant influence on
the nature of the local interstellar space for a long distance up to the
heliopause. As a well established scientific discipline, solar and space
physics aims to understand the history, evolution, and physical behavior
of the most influential object in - and its impact on the dynamics of -
the space environment around our home planet.

% is not only
% a matter of scientific curiosity.
% Therefore, as a well established scientific discipline,
% solar and space physics aims to understand the history, evolution, and
% physical behavior of the most influential object in the space environment
% around our home planet.
